---
title: "Group 38 UCSB domestic grad enrollment"
author: "Conner Smith, Sam Kuglen"
date: "11/12/2021"
output: 
  html_document: 
    toc: yes
    toc_depth: 2
    theme: flatly
---

## **Overview**

This report explores domestic graduate enrollment (individual counts) at UCSB by race / ethnicity from 2008 - 2019. The data comes directly from the [UCSB Office of Budget and Planning Campus Profiles.](https://bap.ucsb.edu/institutional-research/campus-profiles)

## **Setup**
```{r setup, include=TRUE, message =FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Attach Packages.

library(tidyverse)
library(here)
```

```{r}
# 2A: Read in the data. 
ucsb_grad <- read_csv(here("data", "ucsb_grad_data.csv"))

# Pushing all changes to Github for partner to complete next step. 

```

## **Change in Graduate Student Enrollment over Time** 

```{r}
# 2B: Added column graph showing change in domestic graduate enrollment.
# 2C: Added a new command to change the position to "fill" and added axis labels.
# 2D: Added graph title, set theme to `theme_minimal`, added figure caption
ggplot(ucsb_grad) +
  geom_col(aes(x = year_abbr, 
               y = domestic_enrollment, 
               fill = ethnicity), 
           position = "fill") +
  labs(x = "Year", 
       y = "Domestic Enrollment",
       title = "UC Santa Barbara Domestic Graduate Student Enrollment",
       subtitle = "2008 - 2019") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5)) +
  guides(fill = guide_legend("Ethnicity")) # update legend title
```

**Figure 1.** UC Santa Barbara domestic graduate student enrollment from 2008 - 2014. Data: UCSB Office of Budget and Planning Campus Profiles.
